---
title: "Lab 01 - Hello R"
author: "Marcus Minko"
date: "1/18/2022"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

1846 rows and 3 variables (dataset, x-values, and y-values)

### Exercise 2

The answers for this exercise are given for you below.
But you should clean up some of the narrative so that it only includes what you want to turn in.

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=5, fig.width=7}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
r = -.0645

### Exercise 3


```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
 ggplot(data = star_data, mapping = aes(x = x, y = y)) + 
   geom_point()
```

The star data plotted clearly shows the outline of a star.

```{r cor-star}
star_data %>%
   summarize(r = cor(x,y))  
```
r = -.063 which is roughly the same as the dino correlation despite being very different visually.
### Exercise 4

Plotting the circle data

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
 ggplot(data = circle_data, mapping = aes(x = x, y = y)) + 
   geom_point()
```
Correlation x and y circle data
```{r cor-circle}
circle_data %>%
   summarize(r = cor(x,y))
```
r = -.068 which is also similar to the previous two examples
### Exercise 5
Plotting all the data
```{r plot-all}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```
All of the summary correlation coefficients
``` {r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

## Bonus Tips by Yoo Ri
Here are some helpful tips :) 

* filter() is for extracting rows

* group_by() is for grouping datasets by assigned column 
* ungroup() cancels the grouping 

* summarize()  is often used with group_by(). This function can print the output according to the group_by().

* facet_grid(y~x,...) creates a grid with variable y as a row, variable x as a column  
* facet_wrap(x,... ) is useful when there is only one variable
